Stable Hot Spot Analysis (Draft)

### 2017-06-17 paper-main.tex
fixed some todos

\author{
  Marc Gassenschmidt \and
  Viliam Simko  \and
  Julian Bruns
  \\
  \email{todo@fzi.de},
  \email{simko@fzi.de},
  \email{bruns@fzi.de}
}

@@

The results can be found in Fig.~\ref{fig:Zoom}. It can be seen that with an
increase of the aggregation level the values increase. TODO if clusters
increase/decrease For the upward property, $G^*$ is always better than Focal
$G^*$, compared to the results from figure \ref{fig:SoHZoom}. Focal $G^*$
reaches the same result as $G^*$ at aggregation level~5 . For the downward
property, Focal $G^*$ leads to better results at aggregation level~5.

>>>>

\author{
  Marc Gassenschmidt \and
  Viliam Simko  \and
  Julian Bruns
  \\
  \email{marcgassenschmidt@googlemail.com},
  \email{simko@fzi.de},
  \email{bruns@fzi.de}
}

@@

The results can be found in Figure~\ref{fig:Zoom}. It can be seen that with an
increase of the aggregation level the values increase. 
%TODO: there was some todo in the text for the following sentence
If clusters
increase/decrease For the upward property, $G^*$ is always better than Focal
$G^*$, compared to the results from figure \ref{fig:SoHZoom}. Focal $G^*$
reaches the same result as $G^*$ at aggregation level~5 . For the downward
property, Focal $G^*$ leads to better results at aggregation level~5.
